How to Analyze Build Logs --- A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-24 tse-paper/content.tex
mention fw and update intro argumentation

To answer this question, we start the investigation by performing an
extensive literature study (\Cref{fig:overview}).
It shows that
less than half of the 61 works which rely on build log analysis
describe in detail how they performed it.
Even fewer
made their implementation available.
The literature
survey identifies three prevalent strategies to
analyze build logs: Using 1) a set of
manually curated regular expressions,
similar to TravisTorrent~\cite{beller2017oops},
2) information
retrieval techniques,
% TODO: Can you shortly explain the technique here?
and 3) a list of search keywords
to identify regions of interest in the build log.

Even though these three approaches to retrieve information chunks from
build logs have different strengths and weaknesses, the literature
survey shows that their use often seems arbitrary.
As a consequence,
in RQ2 we ask:

@@

To answer this question, in the second step of the study
(\Cref{fig:overview}), we build and compare three
implementations that each stand prototypical for one of the identified
strategies to analyze build logs:

\begin{itemize}
  \item \textbf{Program Synthesis by Example (referred to as PBE)}
  Based on manually supplied example pairs of build logs and chunks,
  PBE automatically
  synthesizes
  a regular expression extracting the given chunks within the build logs.
  \item \textbf{Common Text Similarity (CTS)}
  CTS selects lines of a log which are
  most similar to the lines present in manually supplied example chunks.
  \item \textbf{Keyword Search (KWS)}
  KWS finds fitting passages by searching the whole
  text of a build log for
  the occurrence of specific trigger words.
\end{itemize}

In the third step, we conduct an empirical study to gauge the performance
of
these chunk retrieval techniques in
real-world projects under a variety of conditions.
Our study is based on the \emph{LogChunks} data
set~\cite{brandt2020logchunks}, which encompasses build logs from
80 popular open-source projects and a broad range of different
build tools and programming languages.

Finally, we develop a set of guidelines (step 4) on how to choose a
technique given a goal.
We recommend PBE for use cases where the desired information is always
represented in the same structural way and high confidence in
precision and recall of the chunk retrieval is required.
Results
produced by PBE are suited for automatic on-ward processing.
CTS is
well-suited when the representation of the desired information varies
slightly and the output of the chunk retrieval is further processed by
a human.
In cases where the textual representation of the desired
information in the log is unpredictable or varies greatly, KWS seems
to be the best choice.
However, its low precision---it extracts a
context of multiple lines around a finding---makes it generally
unsuited for automatic on-ward processing.
Instead, KWS requires a human
to further inspect and interpret the output chunk.
A hybrid-solution combining the three techniques might be the best
all-round solution.

In short, this article contributes
\begin{itemize}
\item the first systematic study of the emerging field of build log
analysis.
\item three prototypical open-sourced implementations of the most
promising chunk retrieval techniques.
\item a large empirical study comparing the three techniques.
\item systematic guidelines on when to use which technique.
\item a detailed replication package~\cite{brandt2020chunk-replication}.
\end{itemize}

@@

\section{Future Work}
% TODO Actually, this future work is very, *very* good.
%It might be
% the best future work I have ever read in an article.
% One idea would be to sell it as such and tie a bit back to our
% first literature sruvey.
%You can say you give a roadmap to guide
% future research in the field, and sell it in abstract and intro!

>>>>

To answer this question, we start the investigation by performing an
extensive literature study (\Cref{fig:overview}).
It shows that
less than half of the 61 works which rely on build log analysis
describe in detail how they performed it.
Even fewer
made their implementation available.
The literature
survey identifies various strategies to
analyze build logs such as:
custom built parsers, regular expressions, manual inspection,
natural language processing, information retrieval or searching
for keywords.
%Using 1) a set of
% manually curated regular expressions,
% similar to TravisTorrent~\cite{beller2017oops},
% 2) information
% retrieval techniques,
% % todo: Can you shortly explain the technique here?
% and 3) a list of search keywords
% to identify regions of interest in the build log.

Even though these three approaches to analyze
build logs have different strengths and weaknesses, the literature
survey shows that their use often seems arbitrary.
As a consequence,
in the second research question we ask:

@@

To answer this question, in the second step of the study
(\Cref{fig:overview}), we choose three promising
techniques to analyze build logs by retrieving substrings
(chunks) that describe a specific information.

We build and compare three
implementations that each stand prototypical for one of the identified
strategies to analyze build logs:

\begin{itemize}
  \item \textbf{Program Synthesis by Example (referred to as PBE)}
  Based on manually supplied example pairs of build logs and chunks,
  PBE automatically synthesizes
  a regular expression extracting the given chunks within the build logs.
  % these second sentences about what the techniques stand for could
  % also be merged to a paragraph after the itemize
  PBE mimics regular expressions and parsers while
  simplifying their development.
  \item \textbf{Common Text Similarity (CTS)}
  Text similarity is a common information retrieval technique.
  CTS selects lines of a log which are
  most similar to the lines present in manually supplied example chunks.
  As a common information retrieval technique, our text similarity
  approach stands for the machine learning approaches identified in
  the literature survey.
  \item \textbf{Keyword Search (KWS)}
  KWS finds fitting passages by searching the whole
  text of a build log for
  the occurrence of specific trigger words.
  Keyword Search was explicitly mentioned by several articles in the
  literature survey.
\end{itemize}

In the third step (\Cref{fig:overview}),
we conduct an empirical study to gauge the performance
of these chunk retrieval techniques in
real-world projects under a variety of conditions.
Our study is based on the \emph{LogChunks} data
set~\cite{brandt2020logchunks}, which encompasses build logs from
80 popular open-source projects and a broad range of different
build tools and programming languages.

We develop a set of guidelines (step 4, \Cref{fig:overview})
on how to choose a
technique given a goal.
We recommend PBE for use cases where the desired information is always
represented in the same structural way and high confidence in
precision and recall of the chunk retrieval is required.
The results PBE produces are suited for automatic on-ward processing.
CTS is
well-suited when the representation of the desired information varies
slightly and the output of the chunk retrieval is further processed by
a human.
In cases where the textual representation of the desired
information in the log is unpredictable or varies greatly, KWS seems
to be the best choice.
However, its low precision---it extracts a
context of multiple lines around a finding---makes it generally
unsuited for automatic on-ward processing.
Instead, KWS requires a human
to further inspect and interpret the output chunk.
A hybrid-solution combining the three techniques might be the best
all-round solution.
Finally, we give a roadmap to guide future research in the field
of build log analysis.

In short, this article contributes
\begin{itemize}
\item the first systematic study of the emerging field of build log
analysis.
\item three prototypical open-sourced implementations of
promising chunk retrieval techniques.
\item a large empirical study comparing the three techniques.
\item systematic guidelines on when to use which technique.
% TODO: is the future work good enough to put in contributions?
\item a detailed replication package~\cite{brandt2020chunk-replication}.
\end{itemize}

@@

\section{Future Work}
% Actually, this future work is very, *very* good.
%It might be
% the best future work I have ever read in an article.
% One idea would be to sell it as such and tie a bit back to our
% first literature sruvey.
%You can say you give a roadmap to guide
% future research in the field, and sell it in abstract and intro!
